---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(seqbtests)
```

This Vignette is supposed to give you a short an easy introduction to the 
seqbtest package. 
The purpose of the package is to provide a flexible and simple to use framework 
to evaluate the performance of benchmark results.

# Introduction 

This package implements different Bayesian tests to compare the performance of 
Machine Learning Algorithms. The performance of the algorithms to be compared 
can be built up within the packages by a function written by the user and can be
directly compared within the tests. For this purpose, the sequential Bayesian 
tests are provided, in which the number of generated performance values does not
have to be fixed at the beginning. Instead, after each replication it is checked 
whether there is a 95% probability to determine which algorithm performs better. 
If this threshold is reached, the build-up of replications is stopped early, 
which can result in significant time savings. These tests work either on a 
single or multiple data sets. Further, some standard Hypothesis tests are 
provided. 



```{r}
plot_boxplot(df = test_benchmark_small)

```


